---
title: "DATA PRODUCTS"
author: "Varun Negi"
date: "1 May 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

This presentation is a part of deliverable required for Data Products Course week 4 project.

# Web Application

This web application calculates linear regression of different variables at MTCars data set. The application provides user with three different inputs:

Select first variable of the regression either:

Mile per Gallon (mpg),
or Horse Power (hp),
Select second variable one of three:

Cylinders,
Transmission,
and Gears
User can select if he\ she wants to show straight line representing linear prediction or not.

# Getting Data

This is the data of MTCars Dataset with various columns where we build a linear regression model among variables across all data at the dataset.
```{r}
head(mtcars)
```
# Linear Regression (mpg ~ cyl)

```{r}
data("mtcars")
 mtcars.cyl.formula <- mpg ~ cyl
    mtcars.cyl.lm <- lm(formula=mtcars.cyl.formula, data=mtcars)
     
```    

# Scatterplot
```{r}      
plot(mtcars.cyl.formula, data=mtcars)
abline(mtcars.cyl.lm,col="Red")
```